### 2021-04-21 SupplementaryMaterial/Vita.tex
Updates from Overleaf

  \section*{Publications}
  \begin{enumerate}
    \item \textbf{Qinkun Bao}, Zihao Wang, Xiaoting Li, James Larus, and Dinghao Wu, ``Abacus: Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering (ICSE 2021)}. (Technical Track)
    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis", In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}. (Artifact)

>>>>

  \section*{Publications}
  \begin{enumerate}
    \item \textbf{Qinkun Bao}, Zihao Wang, Xiaoting Li, James Larus, and Dinghao Wu, ``Abacus: Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering (ICSE 2021)}. (Technical Track)
    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}. (Artifact)
